---
title: "nmel_phys"
author: "K Hunter"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(ggplot2)
library(rcompanion)
library(nortest)
library(lme4)
library(lmerTest)
library(nlme)
library(ggsignif)  
library(emmeans)
library(Rmisc)
library(multcomp)
setwd("~/Box Sync/Nomia_protocols_analyses/nomia/effects_analyses/nmel_phys")
m <- read_csv("~/Box Sync/Nomia_protocols_analyses/nomia/original_data_sheets/compiled_nomia_data.csv")

m$ecoli<-revalue(m$ecoli, c("1"="Control", "2"="Ringers", "3"="E. coli"))
m$ecoli<-factor(m$ecoli, levels=c("Control", "Ringers", "E. coli"))
m$dufours.length<-as.numeric(as.character(m$dufours.length))
```



#Set up document with oocyte stages
```{r, echo=FALSE, include=FALSE}
m$left.resorbing.oocyte<-as.numeric(as.character(m$left.resorbing.oocyte))
m$right.resorbing.oocyte<-as.numeric(as.character(m$right.resorbing.oocyte))
m$left.resorbing.trophocyte<-as.numeric(as.character(m$left.resorbing.trophocyte))
m$right.resorbing.trophocyte<-as.numeric(as.character(m$right.resorbing.trophocyte))

#Changing any -- to NAs
levels(m$right.resorbing.trophocyte)[levels(m$right.resorbing.trophocyte)=="--"] <- NA
levels(m$left.resorbing.trophocyte)[levels(m$left.resorbing.trophocyte)=="--"] <- NA
levels(m$left.resorbing.oocyte)[levels(m$left.resorbing.oocyte)=="--"] <- NA
levels(m$right.resorbing.oocyte)[levels(m$right.resorbing.oocyte)=="--"] <- NA

#Making the na's into a 0. 
m$left.resorbing.trophocyte[is.na(m$left.resorbing.trophocyte)] <- 0
m$right.resorbing.trophocyte[is.na(m$right.resorbing.trophocyte)] <- 0

#summing into full egg chamb
m$left.resorb.egg.chamb<-apply(m[,c('left.resorbing.trophocyte', 'left.resorbing.oocyte')],1,function(x)sum(x))
m$right.resorb.egg.chamb<-apply(m[,c('right.resorbing.trophocyte', 'right.resorbing.oocyte')],1,function(x)sum(x))

#finding percentage of oocyte chamber
m$left.percentage.resorbing<-(m$left.resorbing.oocyte/m$left.resorb.egg.chamb)
m$right.percentage.resorbing<-(m$right.resorbing.oocyte/m$right.resorb.egg.chamb)

#picking the max of the two percentages 
m$max_percentage_resorbing<-pmax(m$left.percentage.resorbing,m$right.percentage.resorbing, na.rm=TRUE)

m$max_stage<-m$max_percentage_resorbing

m$max_stage[(m$max_stage)==1] <- "5r"
m$max_stage[(m$max_stage)<1] <- "4r"

#Making the max stage of non-resorbing

m$left.oocyte<-as.numeric(as.character(m$left.oocyte))
m$left.trophocyte<-as.numeric(as.character(m$left.trophocyte))
m$right.oocyte<-as.numeric(as.character(m$right.oocyte))
m$right.trophocyte<-as.numeric(as.character(m$right.trophocyte))

m$left.egg.chamb<-apply(m[,c('left.trophocyte', 'left.oocyte')],1,function(x)sum(x))
m$right.egg.chamb<-apply(m[,c('right.trophocyte', 'right.oocyte')],1,function(x)sum(x))
#finding percentage of oocyte chamber
m$left.percentage<-(m$left.oocyte/m$left.egg.chamb)
m$right.percentage<-(m$right.oocyte/m$right.egg.chamb)
#picking the max of the two percentages 
m$max_percentage_nonr<-pmax(m$left.percentage,m$right.percentage, na.rm=TRUE)

m$max_stage_nonr<-m$max_percentage_nonr

m$max_stage_nonr[(m$max_stage_nonr)<.45] <- "1_2"
m$max_stage_nonr[(m$max_stage_nonr)<.551] <- "3"
m$max_stage_nonr[(m$max_stage_nonr)<1] <- "4"

for (i in 1:length(m$max_stage)){
  if (is.na(m$max_stage[i])){
    m$max_stage[i]<-m$max_stage_nonr[i]
  }
}

m$max_stage<-as.factor(m$max_stage)
stage_complete<-m[complete.cases(m$max_stage),]
#need to change those that assign as 1_2 to either 1 or 2
table(stage_complete$Beeid, stage_complete$max_stage, stage_complete$timespan_tx)
#A07.18019-Stage 1 
#H01.18047-Stage 2
#H01.18073-Stage 2
#H02.18024-Stage 2
#H02.18027-Stage 1
stage_complete$max_stage<-as.character(stage_complete$max_stage)
stage_complete$max_stage[stage_complete$Beeid=="A07.18019"]<-"1"
stage_complete$max_stage[stage_complete$Beeid=="H01.18047"]<-"2"
stage_complete$max_stage[stage_complete$Beeid=="H01.18073"]<-"2"
stage_complete$max_stage[stage_complete$Beeid=="H02.18024"]<-"2"
stage_complete$max_stage[stage_complete$Beeid=="H02.18027"]<-"1"
stage_complete$max_stage<-as.factor(stage_complete$max_stage)


#Include non-resorbing/resorbing oocytes
stage_complete$max_stage
stage_complete$resorb_p.a<-stage_complete$max_stage
stage_complete$resorb_p.a<-as.character(stage_complete$resorb_p.a)
stage_complete$resorb_p.a[stage_complete$resorb_p.a=="4r" | stage_complete$resorb_p.a=="5r"] = "r"
stage_complete$resorb_p.a[!stage_complete$resorb_p.a=="r"]="nonr"
stage_complete$resorb_p.a<-as.factor(stage_complete$resorb_p.a)

stage_complete$ecoli<-as.character(stage_complete$ecoli)
stage_complete$ecoli<-as.factor(stage_complete$ecoli)
stage_complete$timespan_tx <- factor(stage_complete$timespan_tx, levels = c("1", "5", "10","20"))

table(stage_complete$max_stage, stage_complete$timespan_tx)
```

Write with stages so that I can use all of this 
```{r, include=FALSE, echo=FALSE}
write.csv(m, file="compileddata_with_oocytestages.csv")
```
Relevel factors so 5 ends up on the lower end

###oocyte length
```{r}
plotNormalHistogram(m$max_both_nonr_resorb)
ad.test(m$max_both_nonr_resorb)
#really close to normal, just kept?

n<-subset(m, timespan_tx != "R"& timespan_tx!="NE")
n$timespan_tx
plotNormalHistogram(n$max_both_nonr_resorb)
ad.test(n$max_both_nonr_resorb)
#normal!!!
```

```{r}
#Used the below for the paper
oocyleng_mod_paper<-lmer(max_both_nonr_resorb~timespan_tx*ecoli+(1|Headwidth), data=n)
#this gives the error: boundary (singular) fit: see help('isSingular') 
#this is a result of the random effect being too small 
oocyleng_mod_paper<-lm(max_both_nonr_resorb~timespan_tx*ecoli, data=n)
summary(oocyleng_mod_paper)
anova(oocyleng_mod_paper)

length(n)
```
##Nmel oocyte Graph
```{r}
library(plyr)
stderr <- summarySE(data=m, measurevar="max_both_nonr_resorb", groupvars=c("ecoli", "timespan_tx"), na.rm=FALSE,conf.interval=.95, .drop=TRUE)
comparison <- HSD.test(oocyleng_mod_paper,c("ecoli","timespan_tx"), group=TRUE,unbalanced=TRUE)
comparison$groups
plot(comparison)
```

```{r}
# stderr$timespan_tx<-factor(stderr$timespan_tx, levels=c("1", "5", "10", "20"))
# levels(stderr$ecoli)[levels(stderr$ecoli)=="1"] <- "Control"
# levels(stderr$ecoli)[levels(stderr$ecoli)=="2"] <- "Ringers"
# levels(stderr$ecoli)[levels(stderr$ecoli)=="3"] <- "E. coli"
```

```{r}
#geom_text(aes(label=paste("(",Counts,",",Duration,")"),hjust=-1, vjust=-1))
order.group<-comparison$groups[order(rownames(comparison$groups)),]
l<-merge(stderr, order.group, by="max_both_nonr_resorb")
#need to reverse group order because above is reverse of what happens with dufours length CLD


emm_ooc <- emmeans(oocyleng_mod_paper, ~ ecoli * timespan_tx)
comparison_ooc <- pairs(emm_ooc, adjust = "tukey")
summary(comparison_ooc)


cld_result_ooc <- cld(emm_ooc, adjust = "tukey", Letters=letters)
print(cld_result)

```

##Made another graph with sample sizes above it
```{r}
# ggplot(data=l, aes(x=timespan_tx, y=max_both_nonr_resorb, fill=ecoli)) +
#   geom_bar(stat="identity", position=position_dodge())+
# geom_errorbar(aes(ymin=max_both_nonr_resorb-sd, ymax=max_both_nonr_resorb+sd), width=0.2, position=position_dodge(0.9)) + 
#   theme_classic() +
#   geom_text(aes(x=timespan_tx, y=max_both_nonr_resorb+sd, label=paste("N=",l$N, "\n", l$groups)),vjust=-1, position=position_dodge(width=0.9), size=3)+
#   xlab("Timespan treatment (days)")+ylab("maximum terminal oocyte length (mm)+/- standard deviation")+
#   scale_fill_brewer(palette="PuBu")+#Can change colors if necessary 
#   expand_limits(y=c(0,4))+
#   ggsave("oocyte_letters+samplenumbers.png")
```
#making a boxplot
```{r}
#get rid of NE and R and re-level the "Days Alive"
m_graph<-m
m_graph$timespan_tx <- factor(m_graph$timespan_tx, levels = c("1", "5", "10","20"))
m_graph %>% drop_na(timespan_tx)
m_nonas<-m_graph[!is.na(m_graph$timespan_tx),]

#m_nonas$ecoli<-revalue(m_nonas$ecoli, c("1"="Control", "2"="Ringers", "3"="E. coli"))

oocyte_plot<-ggplot(data=m_nonas, aes(x=timespan_tx, y=max_both_nonr_resorb, fill=ecoli)) +
  geom_boxplot() + 
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  theme(axis.title.x = element_text(size=10, face="bold", color = "black"), axis.title.y = element_text(size=10, face="bold", color = "black"))+
  theme(legend.position="none")+
scale_fill_brewer(palette="PuBu", name="Immune Challenge \nTreatment", labels=c("Handling Control", "Injection Control", "Immune Challenge"))+
  geom_text(data=cld_result_ooc, aes(label=.group, y=0.01), 
               position = position_dodge(width = .75), 
               show.legend = FALSE )+
xlab("Age (days)")+ylab("Maximum Terminal Oocyte Length (mm)")
  
ggsave(plot=oocyte_plot, device="png", filename="oocyte_plot.png", path = "figures", height=4, width=4, dpi=1000) 
```

##Fat percentage analysis
```{r, echo=FALSE}
m$fat_percentage<-as.numeric(m$fat_percentage)
ggplot(aes(x = timespan_tx, y=fat_percentage, fill=ecoli), data=m)+
  geom_boxplot()+
  geom_point(position=position_jitterdodge())+
  scale_fill_brewer(palette="Oranges", name="Immune Injection Treatment", labels=c("Handling Control", "Injection Control", "Immune Challenge"))+
  xlab("Days alive")+ylab("Percentage of Abdomen covered in fat")+ggtitle("Immune and Age on fat body")
```
#Based on graph, decided not to do fat body statistical analysis as all measurements were all over the board

Statistical Analysis
```{r}
plotNormalHistogram(m$dufours.length)
ad.test(m$dufours.length)
#normal! 

n<-subset(m, timespan_tx != "R"& timespan_tx!="NE")
n$timespan_tx
plotNormalHistogram(n$dufours.length)
ad.test(n$dufours.length)
#little less normal but fine after all
```

```{r}
summary(step(lm(dufours.length~timespan_tx+ecoli+Headwidth+colonyID+days_since_start_dissect+days_sincestart_wash+initials.of.person.dissecting+bed, data=n), direction="both"))
final.mod<-step(lm(dufours.length~timespan_tx+ecoli+Headwidth+colonyID+days_since_start_dissect+days_sincestart_wash+initials.of.person.dissecting+bed, data=n), direction="both")

duf_mod<-lmer(dufours.length~timespan_tx*ecoli+(1|Headwidth) + (1|bed), data=n)
summary(duf_mod)
anova(duf_mod)


#Used the below for the paper
duf_mod_paper<-lmer(dufours.length~timespan_tx*ecoli+(1|Headwidth), data=n)
summary(duf_mod_paper)
anova(duf_mod_paper)
length(n)

library(multcomp)
summary(glht(duf_mod, linfct = mcp(timespan_tx = "Tukey")), test = adjusted("holm"))
```

#Graph for Dufour's gland
Dufours analysis
```{r, echo=FALSE}

library(emmeans)
emm <- emmeans(duf_mod_paper, ~ ecoli * timespan_tx)
comparison_duf <- pairs(emm, adjust = "tukey")
summary(comparison_duf)

library(multcomp)
cld_result <- cld(emm, adjust = "tukey", Letters=letters)
print(cld_result)
```

```{r}
duf_plot<-ggplot(aes(x = timespan_tx, y=dufours.length, fill=ecoli), data=m_nonas)+
  geom_boxplot()+
  theme_classic()+
  theme(legend.position="right")+
  theme(axis.title.x = element_text(size=10, face="bold", color = "black"), axis.title.y = element_text(size=10, face="bold", color = "black"))+
  geom_point(position=position_jitterdodge())+
    geom_text(data=cld_result, aes(label=.group, y=3), 
               position = position_dodge(width = .75), 
               show.legend = FALSE )+
  scale_fill_brewer(palette="PuBu", name="Immune Challenge \nTreatment", labels=c("Handling Control", "Injection Control", "Immune Challenge"))+
  xlab("Age (days)")+ylab("Dufours Gland Length (mm)")



ggsave(plot=duf_plot, device="png", filename="dufours_plot.png", path = "figures", width=4, height=4, dpi=1000) 
```




#Timespan affects Dufour's Length (unsuprising perhaps)
#New graph to show significant difference
#Was one interaction effect, but only with 3 samples in one interaction, hard to say what's going on-check later

```{r, echo=FALSE}
sigs<-dufplot+
  geom_signif(comparisons=list(c("1", "5")), annotations="NS",
              y_position = 6.4, tip_length = 0, vjust=0.4)+
  geom_signif(comparisons=list(c("1", "10")), annotations="***",
              y_position = 7, tip_length = 0, vjust=0.4)+
  geom_signif(comparisons=list(c("1", "20")), annotations="***",
              y_position = 7.2, tip_length = 0, vjust=0.4)+
  geom_signif(comparisons=list(c("5", "10")), annotations="**",
              y_position = 6.8, tip_length = 0, vjust=0.4)+
geom_signif(comparisons=list(c("5", "20")), annotations="***",
              y_position = 6.6, tip_length = 0, vjust=0.4)

graph_model<-sigs+annotate("text", x=3.5, y=8, label="Model: dufours.length~timespan_tx*ecoli+(1|headwidth) + (1|bed)")

```
