---
title: "nmel_phys"
author: "K Hunter"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(ggplot2)
library(rcompanion)
library(nortest)
library(lme4)
library(lmerTest)
library(nlme)
library(ggsignif)  
library(emmeans)
setwd("~/Box Sync/Nomia_protocols_analyses/nomia/effects_analyses/nmel_phys")
m <- read_csv("~/Box Sync/Nomia_protocols_analyses/nomia/original_data_sheets/compiled_nomia_data.csv")

```

#Set up document with oocyte stages
```{r, echo=FALSE, include=FALSE}
m$left.resorbing.oocyte<-as.numeric(as.character(m$left.resorbing.oocyte))
m$right.resorbing.oocyte<-as.numeric(as.character(m$right.resorbing.oocyte))
m$left.resorbing.trophocyte<-as.numeric(as.character(m$left.resorbing.trophocyte))
m$right.resorbing.trophocyte<-as.numeric(as.character(m$right.resorbing.trophocyte))

#Changing any -- to NAs
levels(m$right.resorbing.trophocyte)[levels(m$right.resorbing.trophocyte)=="--"] <- NA
levels(m$left.resorbing.trophocyte)[levels(m$left.resorbing.trophocyte)=="--"] <- NA
levels(m$left.resorbing.oocyte)[levels(m$left.resorbing.oocyte)=="--"] <- NA
levels(m$right.resorbing.oocyte)[levels(m$right.resorbing.oocyte)=="--"] <- NA

#Making the na's into a 0. 
m$left.resorbing.trophocyte[is.na(m$left.resorbing.trophocyte)] <- 0
m$right.resorbing.trophocyte[is.na(m$right.resorbing.trophocyte)] <- 0

#summing into full egg chamb
m$left.resorb.egg.chamb<-apply(m[,c('left.resorbing.trophocyte', 'left.resorbing.oocyte')],1,function(x)sum(x))
m$right.resorb.egg.chamb<-apply(m[,c('right.resorbing.trophocyte', 'right.resorbing.oocyte')],1,function(x)sum(x))

#finding percentage of oocyte chamber
m$left.percentage.resorbing<-(m$left.resorbing.oocyte/m$left.resorb.egg.chamb)
m$right.percentage.resorbing<-(m$right.resorbing.oocyte/m$right.resorb.egg.chamb)

#picking the max of the two percentages 
m$max_percentage_resorbing<-pmax(m$left.percentage.resorbing,m$right.percentage.resorbing, na.rm=TRUE)

m$max_stage<-m$max_percentage_resorbing

m$max_stage[(m$max_stage)==1] <- "5r"
m$max_stage[(m$max_stage)<1] <- "4r"

#Making the max stage of non-resorbing

m$left.oocyte<-as.numeric(as.character(m$left.oocyte))
m$left.trophocyte<-as.numeric(as.character(m$left.trophocyte))
m$right.oocyte<-as.numeric(as.character(m$right.oocyte))
m$right.trophocyte<-as.numeric(as.character(m$right.trophocyte))

m$left.egg.chamb<-apply(m[,c('left.trophocyte', 'left.oocyte')],1,function(x)sum(x))
m$right.egg.chamb<-apply(m[,c('right.trophocyte', 'right.oocyte')],1,function(x)sum(x))
#finding percentage of oocyte chamber
m$left.percentage<-(m$left.oocyte/m$left.egg.chamb)
m$right.percentage<-(m$right.oocyte/m$right.egg.chamb)
#picking the max of the two percentages 
m$max_percentage_nonr<-pmax(m$left.percentage,m$right.percentage, na.rm=TRUE)

m$max_stage_nonr<-m$max_percentage_nonr

m$max_stage_nonr[(m$max_stage_nonr)<.45] <- "1_2"
m$max_stage_nonr[(m$max_stage_nonr)<.551] <- "3"
m$max_stage_nonr[(m$max_stage_nonr)<1] <- "4"

for (i in 1:length(m$max_stage)){
  if (is.na(m$max_stage[i])){
    m$max_stage[i]<-m$max_stage_nonr[i]
  }
}

m$max_stage<-as.factor(m$max_stage)
stage_complete<-m[complete.cases(m$max_stage),]
#need to change those that assign as 1_2 to either 1 or 2
table(stage_complete$Beeid, stage_complete$max_stage, stage_complete$timespan_tx)
#A07.18019-Stage 1 
#H01.18047-Stage 2
#H01.18073-Stage 2
#H02.18024-Stage 2
#H02.18027-Stage 1
stage_complete$max_stage<-as.character(stage_complete$max_stage)
stage_complete$max_stage[stage_complete$Beeid=="A07.18019"]<-"1"
stage_complete$max_stage[stage_complete$Beeid=="H01.18047"]<-"2"
stage_complete$max_stage[stage_complete$Beeid=="H01.18073"]<-"2"
stage_complete$max_stage[stage_complete$Beeid=="H02.18024"]<-"2"
stage_complete$max_stage[stage_complete$Beeid=="H02.18027"]<-"1"
stage_complete$max_stage<-as.factor(stage_complete$max_stage)


#Include non-resorbing/resorbing oocytes
stage_complete$max_stage
stage_complete$resorb_p.a<-stage_complete$max_stage
stage_complete$resorb_p.a<-as.character(stage_complete$resorb_p.a)
stage_complete$resorb_p.a[stage_complete$resorb_p.a=="4r" | stage_complete$resorb_p.a=="5r"] = "r"
stage_complete$resorb_p.a[!stage_complete$resorb_p.a=="r"]="nonr"
stage_complete$resorb_p.a<-as.factor(stage_complete$resorb_p.a)

stage_complete$ecoli<-as.character(stage_complete$ecoli)
stage_complete$ecoli<-as.factor(stage_complete$ecoli)
stage_complete$timespan_tx <- factor(stage_complete$timespan_tx, levels = c("1", "5", "10","20"))
```

Write with stages so that I can use all of this 
```{r, include=FALSE, echo=FALSE}
write.csv(m, file="compileddata_with_oocytestages.csv")
```

##Fat percentage analysis
```{r, echo=FALSE}
m$fat_percentage<-as.numeric(m$fat_percentage)
ggplot(aes(x = timespan_tx, y=fat_percentage, fill=ecoli), data=m)+
  geom_boxplot()+
  geom_point(position=position_jitterdodge())+
  scale_fill_brewer(palette="Oranges", name="Immune Injection Treatment", labels=c("Handling Control", "Injection Control", "Immune Challenge"))+
  xlab("Days alive")+ylab("Percentage of Abdomen covered in fat")+ggtitle("Immune and Age on fat body")
```
#Based on graph, decided not to do fat body statistical analysis as all measurements were all over the board

#Graph for Dufour's gland
Dufours analysis
```{r, echo=FALSE}
m$dufours.length<-as.numeric(as.character(m$dufours.length))
dufplot<-ggplot(aes(x = timespan_tx, y=dufours.length, fill=ecoli), data=m)+
  geom_boxplot()+
  geom_point(position=position_jitterdodge())+
  scale_fill_brewer(palette="Oranges", name="Immune Injection Treatment", labels=c("Handling Control", "Injection Control", "Immune Challenge"))+
  xlab("Days alive")+ylab("Dufours Gland Length (mm)")+ggtitle("Immune and Age on Dufour's Gland")
```
Statistical Analysis
```{r}
plotNormalHistogram(m$dufours.length)
ad.test(m$dufours.length)
#normal! 
#Need to remove the NEs and Rs

n<-subset(m, timespan_tx != "R"& timespan_tx!="NE")
n$timespan_tx
plotNormalHistogram(n$dufours.length)
ad.test(n$dufours.length)
#little less normal but fine after all
```

```{r}
summary(step(lm(dufours.length~timespan_tx+ecoli+Headwidth+colonyID+days_since_start_dissect+days_sincestart_wash+initials.of.person.dissecting+bed, data=n), direction="both"))
final.mod<-step(lm(dufours.length~timespan_tx+ecoli+Headwidth+colonyID+days_since_start_dissect+days_sincestart_wash+initials.of.person.dissecting+bed, data=n), direction="both")

duf_mod<-lmer(dufours.length~timespan_tx*ecoli+(1|Headwidth) + (1|bed), data=n)
summary(duf_mod)
anova(duf_mod)

library(multcomp)
summary(glht(duf_mod, linfct = mcp(timespan_tx = "Tukey")), test = adjusted("holm"))
```

#Timespan affects Dufour's Length (unsuprising perhaps)
#New graph to show significant difference

```{r, echo=FALSE}
sigs<-dufplot+
  geom_signif(comparisons=list(c("1", "5")), annotations="NS",
              y_position = 6.4, tip_length = 0, vjust=0.4)+
  geom_signif(comparisons=list(c("1", "10")), annotations="***",
              y_position = 7, tip_length = 0, vjust=0.4)+
  geom_signif(comparisons=list(c("1", "20")), annotations="***",
              y_position = 7.2, tip_length = 0, vjust=0.4)+
  geom_signif(comparisons=list(c("5", "10")), annotations="**",
              y_position = 6.8, tip_length = 0, vjust=0.4)+
geom_signif(comparisons=list(c("5", "20")), annotations="***",
              y_position = 6.6, tip_length = 0, vjust=0.4)

graph_model<-sigs+annotate("text", x=3.5, y=8, label="Model: dufours.length~timespan_tx*ecoli+(1|headwidth) + (1|bed)")

```

Oocyte analysis
```{r}
```

Fat body analysis
